---
title: "Figure 1 for Deleterious Alleles paper"
output: pdf_document
---

```{r setup, include=TRUE}
#setwd("~/Documents/Github/pvpDiallel/")
knitr::opts_knit$set(root.dir=normalizePath('../'))
```

To reproduce the figures, we should set `pvpDiallel` as the root path, i.e. `setwd("~/Documents/Github/pvpDiallel/")`. And then use `knitr` package to knit a pdf file. Or simplely click `Knit PDF` icon in `RStudio`. Note, to generate each panel into seperate pdf files, we should turn `getpdf` into `TRUE` (i.e. `getpdf=TRUE`) when calling the plotting functions.

First of all, determine fond size and set the getpdf option:
```{r}
#par(mar=c(5,4,4,2))
par(font= 2, font.lab= 2, font.axis= 2)
fs <- 1.6 # times bigger than default
ht= 6; wt= 6 #figure height and weight
getpdf <- TRUE # get figures in seperated pdf [TRUE] or not [FALSE]
```


# Figure 1a

```{r, eval=TRUE, fig.width=ht, fig.height=wt}
plotloh <- function(getpdf, outfile, ...){
  trait <- read.csv("data/hyb_heterosis.csv")
  trait$pMPH <- abs(trait$pMPH*100)
  bymed2 <- with(trait, reorder(trait, pMPH, median))
  boxplot(pMPH ~ bymed2, data=trait,
          xlab = "", ylab= "MPH (100%)", col="antiquewhite3", 
          ...)
  if(getpdf == TRUE){
    pdf(outfile, width=ht, height=wt)
    par(mar=c(5,5,4,2))
    boxplot(pMPH ~ bymed2, data=trait,
          xlab = "", ylab= "Mid-Parent Heterosis (100%)", col="antiquewhite3", 
          ...)
    dev.off()
  }
}

plotloh(getpdf, outfile="graphs/Fig1a.pdf",
        main="", cex.axis=fs, cex.lab=fs, las=2)
```

# Figure 1b

```{r, eval=TRUE, fig.width=ht, fig.height=wt}
plot_load <- function(getpdf, outfile, ...){
  dres <- read.table("data/sup_deleterious_hmp3.txt", header=T)
  
  boxplot(DR ~ geno*ordered, data=dres, border=c("darkgreen","darkblue"), col="grey",  ...)
  #text(cex=fs, x=x-.25, y=-1.25, H2$Traits, xpd=TRUE, srt=45, pos=2)
  if(getpdf == TRUE){
    pdf(outfile, width=ht, height=wt)
    par(mar=c(5,5,4,2))
    boxplot(DR ~ geno*ordered, data=dres, border=c("darkgreen","darkblue"), col="grey",  ...)

    box()
    dev.off()
  }
}

plot_load(getpdf, outfile="graphs/Fig1d_v3.pdf",
          names=c("LR", "MZ", "LR", "MZ", "LR", "MZ"),
          xlab="", ylab="Deleterious Load per bp",
          main="", cex.axis=fs, cex.lab=fs)

```

# Figure 1c

```{r, eval=TRUE, fig.width=ht, fig.height=wt}
plotReg <- function(getpdf, outfile, ...){
  snptab <- read.csv("cache/daf_gerp2.csv")
  snptab <- snptab[order(snptab$GERP2),]
  plx <- predict(loess(snptab$meandaf ~ snptab$GERP2), se=T)
  x <- snptab$GERP2
  y <- snptab$meandaf
 
  plot(x, y, ...)
  lines(snptab$GERP2, plx$fit, col="cornflowerblue", lwd=2)
  lines(snptab$GERP2, plx$fit - qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
  lines(snptab$GERP2, plx$fit + qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
  
  if(getpdf == TRUE){
    pdf(outfile, width=wt, height=ht)
    par(mar=c(5,5,4,2))
    plot(x, y, ...)
    lines(snptab$GERP2, plx$fit, col="cornflowerblue", lwd=2)
    lines(snptab$GERP2, plx$fit - qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
    lines(snptab$GERP2, plx$fit + qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
  
    dev.off()
  }
}

plotReg(getpdf, outfile="graphs/Fig1b_v3.pdf",
        pch=16, col="antiquewhite3", xlab="GERP Score", ylab="Allele Frequency", 
        main="", cex.axis=fs, cex.lab=fs)
```

# Figure 1d


```{r, eval=TRUE, fig.width=wt, fig.height=ht}
##########################
plotmgerp <- function(mgerp, getpdf, outfile, ...){
    
    #mgerp <- read.csv("cache/mgerp_cm.csv")
    
    mgerp <- mgerp[order(mgerp$gen),]
    plx <- predict(loess(mgerp$mgerp ~ mgerp$gen), se=T)
    x <- mgerp$gen
    y <- mgerp$mgerp
    
    plot(x, y, ...)
    lines(mgerp$gen, plx$fit, col="cornflowerblue", lwd=2)
    lines(mgerp$gen, plx$fit - qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
    lines(mgerp$gen, plx$fit + qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
    
    if(getpdf == TRUE){
        pdf(outfile, width=wt, height=ht)
        par(mar=c(5,5,4,2))
        plot(x, y, ...)
        lines(mgerp$gen, plx$fit, col="cornflowerblue", lwd=2)
        lines(mgerp$gen, plx$fit - qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
        lines(mgerp$gen, plx$fit + qt(0.975,plx$df)*plx$se, lty=2, lwd=2, col="black")
        
        dev.off()
    }
}

mgerp <- read.csv("cache/mgerp_cm.csv")
plotmgerp(mgerp, getpdf=TRUE, outfile="graphs/Fig1d.pdf",
        pch=16, col="antiquewhite3", xlab="Recombination Rate (cM/Mb)", ylab="GERP Score", 
        main="", cex.axis=fs, cex.lab=fs)
```




